%-------------------------
% Resume in LaTeX
% Author : Adrien Lacquemant
% License : MIT
%------------------------

\documentclass[letterpaper,10pt,usenames,dvipsnames]{article}

% Packages
\usepackage{latexsym, fullpage, titlesec, marvosym, verbatim, enumitem, hyperref, background, color}

% Adjust margins
\addtolength{\oddsidemargin}{-0.25in}
\addtolength{\evensidemargin}{-0.25in}
\addtolength{\textwidth}{0.5in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.2in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-5pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeItemSimple}[1]{
  \item\small{
    {#1}{\vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\newcommand{\engineerType}{Senior Software Engineer}
\newcommand{\email}{adrien@alaq.io}
\newcommand{\address}{Brooklyn, NY 11222}

% Add these lines before \begin{document}
\newcommand{\watermarkContent}{CONFIDENTIAL}
\newif\ifshowwatermark
\showwatermarkfalse % Set to \showwatermarktrue or \showwatermarkfalse to show or hide watermark and notice

% Modify the \backgroundsetup command
\backgroundsetup{
  scale=5,
  color=black!10,
  angle=45,
  opacity=0.05,
  contents={\ifshowwatermark\watermarkContent\fi}
}

% CV STARTS HERE
\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{http://alaq.io/}{\Large Adrien Lacquemant}} \textit{\engineerType{}} & \address{}\\
  \href{https://alaq.io}{alaq.io} -- \href{https://github.com/alaq}{github.com/alaq} -- \href{https://www.linkedin.com/in/adrien-lacquemant/}{linkedin.com/in/adrien-lacquemant/} & \href{mailto:\email{}}{\email{}} -- +1 (646) 410-3409 \\
\end{tabular*}

%--------SUMMARY------------
\section{Summary}
Experienced senior software engineer with expertise in large-scale distributed systems. Known for innovative problem-solving and project management, I excel in developing scalable code and leading diverse teams, focusing on continuous improvement and crafting technically precise, user-centric applications. Excited to join a dynamic team, utilizing my experience in large system architecture to address challenging problems.

\section{Core and Technical Competencies}
Software Engineering | Project Management | Team Leadership | Continuous Improvement | Process Optimization | Documentation | Distributed Systems | Scalable Code Development | Cross-Functional Coordination | Quality Assurance

%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {WhatsApp (Meta)}{New York, NY}
      {Senior Software Engineer - Backend - Group Messaging and Communities}{April 2022 - April 2023}
      \resumeItemListStart
        \resumeItemSimple{Launched Communities feature, improving user engagement and adoption targets.}
        \resumeItemSimple{Contributed to key backend projects, including Group Join Request, enhancing user experience for WhatsApp's extensive 2.5 billion user base.}
        \resumeItemSimple{Championed a cross-functional effort to transition user identifiers from phone numbers to internal identifiers, significantly enhancing system resilience and user privacy.}
        \resumeItemSimple{Improved existing endpoint latencies by up to 40\% in the context of Communities, markedly improving response times and system performance.}
        \resumeItemSimple{Developed and integrated GDPR-compliant reporting features, upholding WhatsApp's adherence to strict data protection regulations.}
        \resumeItemSimple{Served as an on-call support engineer for critical systems (group messaging backend), optimized the process, highlighted inefficiencies, effectively mitigated outages, and reduced impact on system performance.}
      \resumeItemListEnd

    \resumeSubheading
      {Bloomberg L.P.}{New York, NY}
      {Senior Software Engineer - Trading \& Analytics}{May 2018 - March 2022}
      \resumeItemListStart
        \resumeItemSimple{Designed, built and released new features to Bloomberg's full stack trading platform framework, while maintaining system stability.}
        \resumeItemSimple{Led cross-functional team projects, consistently delivering them in alignment with established timeframes.}
        \resumeItemSimple{Drove the adoption of new technologies, focusing on modern frameworks and languages like TypeScript and React.}
        \resumeItemSimple{Led the improvement of development practices, emphasizing efficient state-management and code modularity.}
        \resumeItemSimple{Mentored others and encourage knowledge sharing in order to drive the growth of the team.}
      \resumeItemListEnd

    \resumeSubheading
      {Fullstack Academy of Code \normalfont\textit{-- major coding bootcamp}}{New York, NY}
      {Teaching Fellow}{Dec 2017 - Apr 2018}
      \resumeItemListStart
        \resumeItemSimple{Led code reviews and acted as a project manager for 4 teams of junior software engineers.}
        \resumeItemSimple{Code paired, debugged/mentored technical concepts and best practices to 50 students on a daily basis.}
        \resumeItemSimple{Conducted technical interviews in JavaScript for prospective students 2 to 3 times a week.}
      \resumeItemListEnd

    \resumeSubheading
      {RecirQ \normalfont\textit{-- electronics wholesaler}}{New York, NY}
      {\engineerType{}}{May 2016 - Apr 2018}
      \resumeItemListStart
      	\resumeItemSimple{Design and implemented a re-engineering project to improve/automate asset processing and tracking, reducing processing time by 25\%.}
        \resumeItemSimple{Developed an in-house SaaS for systematic asset and sales monitoring per device leading to 20\% in increased revenue.}
        \resumeItemSimple{Wrote a data validation tool in JavaScript that ensured the accuracy of inventory and sales data feeds.}
      \resumeItemListEnd

    \resumeSubheading
      {BISAM, Inc. \normalfont\textit{-- financial software vendor}}{New York, NY}
      {Product Support Analyst}{Jan 2015 - Apr 2016}
      \resumeItemListStart
        \resumeItemSimple{Troubleshot financial calculation issues raised by clients and Professional Services team.}
        \resumeItemSimple{Supported defect resolution by identifying and replicating bugs.}
        \resumeItemSimple{Tested patch releases and managed deliveries.}
      \resumeItemListEnd

    \resumeSubheading
      {Tortus Capital Management \normalfont\textit{-- value oriented hedge fund}}{New York, NY}
      {Research and Trading Analyst}{Jul 2013 - Jul 2014}
      \resumeItemListStart
        \resumeItemSimple{Completed financial analysis for over 30 distressed companies and recommended long/short positions.}
        \resumeItemSimple{Traded and monitored the firm's securities on a daily basis.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd
  {Previous employers: UBS - Sales Trader \textit{Paris, France}, Credit Suisse - Sales Trader \textit{Paris, France}, France Télévisions Publicité - Business Analyst \textit{Paris, France}}

%-----------PROJECTS-----------------
\section{Projects}
\resumeSubHeadingListStart
  \resumeSubheading
    {Kyozo \normalfont\textit{-- technical advisor}}{\href{https://kyozo.com}{https://kyozo.com}}
    {An instant messaging based platform for communities to reach their audience.}{2023 to 2024}

  \resumeSubheading
    {caltxt \normalfont\textit{-- developer}}{\href{https://caltxt.vercel.app}{https://caltxt.vercel.app}}
    {A vim-keybinded text based client for Google Calendar}{2024}

  \resumeSubheading
    {Monjo \normalfont\textit{-- developer}}{}
    {A checkin app (like Foursquare) for locations, people and events for iOS in Swift.}{2024}

  \resumeSubheading
    {Calendar Tasks \normalfont\textit{-- developer}}{}
    {A time blocking and task management app for iOS in Swift.}{2024}

  \resumeSubheading
    {RoamSync \normalfont\textit{-- founder \& developer}}{\href{https://roamsync.vercel.app}{https://roamsync.vercel.app}}
    {A React and Node.js application that syncs data between Roam Research and Google Calendar.}{}

  \resumeSubheading
    {Athens \normalfont\textit{-- open source contributor}}{\href{https://github.com/athensresearch/athens}{https://github.com/athensresearch/athens}}
    {A knowledge graph for research and notetaking, written in Clojure(script).}{}

  \resumeSubheading
    {Learning Clojure in public \normalfont\textit{-- author}}{\href{https://github.com/alaq/learning-clojure-in-public}{https://github.com/alaq/learning-clojure-in-public}}
    {Learned Clojure in 5 weeks and wrote one blog post per day.}{July 2020}

  \resumeSubheading
    {Propel ML \normalfont\textit{-- open source contributor}}{\href{https://github.com/propelml/propel}{https://github.com/propelml/propel}}
    {GPU-backed numpy-like infrastructure for scientific computing in JavaScript.}{}

  \resumeSubheading
    {Device Extract, LLC. \normalfont\textit{-- founder \& developer}}{}
    {An Electron app for cataloging mobile devices programmatically.}{June 2017 to April 2018}

\resumeSubHeadingListEnd

%-----------EDUCATION-----------------
\section{Education}
\resumeSubHeadingListStart
  \resumeSubheading
    {ESSEC Business School}{Singapore}
    {M.S. Financial Engineering}{2013}
  \resumeSubheading
    {Université Paris Dauphine}{Paris, France}
    {M.S. Finance \& B.S. Management}{2011}
\resumeSubHeadingListEnd

%-----------PROFESSIONAL DEVELOPMENT-----------------
\section{Professional Development}
\resumeSubHeadingListStart
  \resumeSubheading
    {Fullstack Academy of Code}{New York, NY}
    {Software Engineering Immersive Program}{2017}
\resumeSubHeadingListEnd

% At the end of the document, before \end{document}
\ifshowwatermark
\section{Confidentiality Notice}
This document is marked as \watermarkContent{} and should be treated accordingly.
\fi

\end{document}
